sem

### 2023-02-09 scripts/workshop/sem.Rmd
playing around with gam

```{r}
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = cc)) + geom_point() + geom_smooth() + 
  labs(title = "cc ~ temp")
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = log10(size))) + geom_point() + geom_smooth() + 
  labs(title = "log(size) ~ temp")
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = Prevalence)) + geom_point() + geom_smooth() + 
  labs(title = "Prev ~ temp")
comm_data %>% ggplot(.,aes(x=cc, y = Prevalence)) + geom_point() + geom_smooth(method = "lm") + 
  labs(title = "Prev ~ log(cc)")
comm_data %>% ggplot(.,aes(x=log10(size), y = Prevalence)) + geom_point() + geom_smooth(method = "lm") + 
  labs(title = "Prev ~ log(size)")
```

@@

```{r}
cc_temp <- gam(log10(cc) ~ s(MeanWaterTempPredC), data = comm_data)
size_temp <- lm(log10(size) ~ (MeanWaterTempPredC), data = comm_data)
prev_cc <- lm(Prevalence ~ log10(cc) + log10(size), data = comm_data)
prev_temp_cc <- glm(Prevalence ~ log10(cc) + log10(size) + MeanWaterTempPredC, data = comm_data)

@@

>>>>

```{r}
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = cc)) + geom_point() + geom_smooth(method = "lm") + 
  labs(title = "cc ~ temp")
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = log10(size))) + geom_point() + geom_smooth(method = "lm") + 
  labs(title = "log(size) ~ temp")
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = Prevalence)) + geom_point() + geom_smooth(method = "lm") + 
  labs(title = "Prev ~ temp")
comm_data %>% ggplot(.,aes(x=cc, y = Prevalence)) + geom_point() + geom_smooth(method = "lm") + 
  labs(title = "Prev ~ log(cc)")
comm_data %>% ggplot(.,aes(x=log10(size), y = Prevalence)) + geom_point() + geom_smooth(method = "lm") + 
  labs(title = "Prev ~ log(size)")
```

@@

```{r}
cc_temp <- gam(log10(cc) ~ s(MeanWaterTempPredC), data = comm_data, method = "REML")
size_temp <- gam(log10(size) ~ s(MeanWaterTempPredC), data = comm_data, method = "REML")
prev_cc <- lm(Prevalence ~ log10(cc) + log10(size), data = comm_data)
prev_temp_cc <- glm(Prevalence ~ log10(cc) + log10(size) + MeanWaterTempPredC, data = comm_data)

@@

# Playing around with GAM

```{r}
gam_1 <- gam(Prevalence ~ s(MeanWaterTempPredC) + s(log10(cc)) + s(log10(size)), data = (comm_data %>% filter(MeanWaterTempPredC>0)), method = "REML", family = "betar")
```
